Pure Spin Current Injection in Hydrogenated Graphene Structures

### 2017-05-11 mu/article/article.tex
Review 1 sent to BMS

We preset the results for $\mathcal{V}^{\mathrm{ab}}$ for the
C$_{16}$H$_{8}$-alt and C$_{16}$H$_{8}$-up structures being both
noncentrosymmetric semi-infinite carbon systems with 50\% hydrogenation in
different arrangements. The \emph{alt} system has alternating hydrogen atoms on
the upper and bottom sides of the carbon sheet, while the \emph{up} system has H
only on the upper side. We take the hexagonal carbon lattice to be on the $xy$
plane for both structures, and the carbon-hydrogen bonds on the perpendicular
$xz$ plane, as depicted in Figs.
\ref{fig:alt-struc} and \ref{fig:up-struc}.

Using the ABINIT code \cite{gonzeCPC09} we calculated the self-consistent ground
state and the Kohn-Sham states using density functional theory in the local
density approximation (DFT-LDA) with a planewave basis. We used Hartwigsen-
Goedecker-Hutter (HGH) relativistic separable dual-space Gaussian
pseudopotentials \cite{hartwigsenPRB98} including the spin-orbit interaction
needed to calculate $\mu^{\mathrm{abcd}}(\omega)$ (Eq.
\eqref{eq:mu}) and $|\mathcal{V}^{\mathrm{a}}(\omega)|$ (Eq. \eqref{eq:vab}).
%
It is known that using DFT-LDA to calculate the electronic structure of
materials predict a different band gap than the obtained experimentally. A
correction for the band gap energy value can be calculated by other \emph{ab-
initio} methods such as the GW approximation \cite{onidaRMP02} but this is
outside the scope of this paper.
% 
The convergence parameters for the calculations of our results corresponding to
the \emph{alt} and \emph{up} structures are cutoff energies of 65\,Ha and
40\,Ha, respectively. The energy eigenvalues and matrix elements were calculated
using 14452 $\mathbf{k}$ points and 8452 $\mathbf{k}$ points in the irreducible
Brillouin zone (IBZ) and present LDA energy band gaps of 0.72\,eV and 0.088\,eV,
respectively for the \emph{alt} and \emph{up} structures.

@@

In figure \ref{fig:vab-str-comp} we present a comparison of the most intense
responses resulting from evaluate the Eq. \eqref{eq:vab} for the \emph{alt} and
\emph{up} 2D structures vs. CdSe and GaAs bulk structures. As we can see from
this figure the most intense response corresponds to the \emph{up} structure
centered at 0.088\,eV corresponding to the THz radiation and reaching a
spin velocity of 87.16\,Km/s.
% 
In the other hand, for an energy range from 0.66\,eV to 3.0\,eV, corresponding
to energies of the Thz and visible radiation, all the four structures have
contributions in the same order of magnitude.
% 
Starting with the 2D structures we have that the \emph{up} structure has other
two peaks centered at 1.94\,eV and 1.97\,eV reaching spin velocities of
22.2\,Km/s and -29.7\,Km/s, respectively, and the \emph{alt} structure has two
peaks centered at 0.72\,eV and 0.91\,eV reaching spin velocities of -40.2\,Km/s
and -32.9\,Km/s, respectively.
% 
Then, for the bulk structures we have that the CdSe has only one intense
response centered at 0.91\,eV reaching a spin velocity of -26.9\,Km/s, and the
GaAs structure has a large and almost planar zone where the response is held
reaching the maximum for an incoming beam of energy of 2.31\,eV and reaching a
spin velocity of -21.6\,Km/s.
% 
In table \ref{tab:vab-str-comp} we present the comparison of this values for the
2D and bulk structures.
%

@@

We first present two energy ranges for the \emph{up} structure, the first for an
incoming energy beam from 0.0\,eV to 0.2\,eV in the THz radiation range where
the absolute maximum of the $|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$
response is obtained and the second for an energy range from 1.80\,eV to 2.1\,eV
where two local maxima are found.

@@

the Eq. \eqref{eq:vs-mag} using different polarization angles $\alpha$ in the
Eq. \eqref{eq:vab} for the \emph{up} structure. In the figure we have that the
onset of the response starts when the energy of the incoming beam is the same of
the gap energy.

@@

From this figure we obtained that the zone where the maximum response is held
corresponds to a energy range of the incident beam from 0.084\,eV to 0.093\,eV,
corresponding to the THz radiation, and polarization angles $\alpha$ between
$30^{\circ}$ and $45^{\circ}$. Also two local maxima are held for same
polarization angles but for an energy range of the incoming beam between
1.90\,eV and 2.05\,eV corresponding to the THz and visible radiation.

@@

and perpendicular and the the arrows are directed to the value of the response

@@

From Figs. \ref{fig:up-vaz-rag-1} and \ref{fig:up-3d-vsz-1} we have that the

@@

$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)=37.4$\,Km/s coming from the

@@

$\gamma_{\mathrm{z}}(\omega)$ are collinear being this angle $65.5^{\circ}$

@@

then, for this variation in the $\gamma_{\mathrm{z}}(\omega)$ angle the complete
range of $\alpha$ angle is included because this last is almost constant.

@@

Now from Figs. \ref{fig:up-vaz-rag-2} and \ref{fig:up-3d-vsz-2} we have that a

@@

of $|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)=30.3$\,Km/s directed in a
velocity angle $\gamma_{\mathrm{z}}(\omega)=78^{\circ}$ on the $xy$ plane for
the spin polarized in the $z$ direction.

@@

@@

In Fig. \ref{fig:alt-3d-vsb} we present the
$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$ spectra resulting from evaluate
again the Eq. \eqref{eq:vs-mag} vs. the photon energy of the incident beam vs.
the polarization angle $\alpha$ in Eq. \eqref{eq:vab} for the \emph{alt}
structure . In the figure we have that the onset of the response starts when the
energy of the incoming beam is the same of the gap energy.
% 
From this figure we found that the zone where the absolute maximum response is
held corresponds to a energy range from 0.90\,eV to 0.93\,eV, corresponding to
the THz raduation, and polarization angles $\alpha$ between $120^{\circ}$ and
$150^{\circ}$. Also, a local maximum is obtained for the same polarization
angles but for energies between 0.67\,eV and 0.75\,eV.
% 
% %%%%%%%%%%%%%%%%%
% %% 0.0 eV - 0.16 eV
% %% Description of ALT |V_{s^z}| & gamma  vs. alpha agle
% %%%%%%%%%%%%%%%%%
In the top frame of Fig. \ref{fig:alt-vaz-rag} we present in solid line the
result of evaluate $|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$, related to the
left scale, fixing the energy of the incoming beam to 0.912\,eV for which value
the response is maximized for the \emph{alt} structure. In the same figure and
frame we present in dashed line, related to the right scale, the velocity angle
$\gamma_{\mathrm{z}}(\omega)$ and in the bottom frame the corresponding
$\mathcal{V}^{\mathrm{xz}}(\omega)$ and $\mathcal{V}^{\mathrm{yz}}(\omega)$
components. Again, the circled and square boxes indicate the values for which
the polarization angle and the velocity angle are parallel and perpendicular and
with arrows are indicated the corresponding response value.
% 
From this figure and from Fig. \ref{fig:alt-3d-vsb} we have that the absolute
maximum response for the \emph{alt} structure is obtained for an incoming beam
with polarization angle $\alpha=145^{\circ}$ reaching a velocity of
$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)=43.0$\,Km/s and for the spin
polarized in the $\mathrm{z}$ direction and resulting in a velocity angle
$\gamma_{\mathrm{z}}(\omega)=50^{\circ}$ on the $xy$ plane. The circled box for
the collinear angle corresponds for angles $\alpha$ and
$\gamma_{\mathrm{z}}(\omega)$ equal to $53.5^{\circ}$ with a value of
$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)=12.7$\,Km/s, and the blue square
box indicates the perpendicular angles for values $\alpha=140^{\circ}$ and
$\gamma_{\mathrm{z}}(\omega)=50^{\circ}$ with a value of
$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)=43$\,Km/s. Finally we found that
for variations of $\pm0.5^{\circ}$ of those collinear and perpendicular angles,
presented with the error bars on the boxes, correspond ranges for the
polarization angle $30^{\circ} \leq \alpha \leq 70^{\circ}$ and $95^{\circ} \leq
\alpha \leq 175^{\circ}$ because the response angle
$\gamma_{\mathrm{z}}(\omega)$ has small variations for the complete range of the
polarization angle $\alpha$.

@@

% %%%%%%%%%%%%%%%%%
% %% 0.0 eV - 0.16 eV
% %% Description of UP |V^{a}| 3D
% %%%%%%%%%%%%%%%%%
For the \emph{up} structure we first analyzed the energy range from 0.00\,eV to
0.16\,eV, where we found the most intense response and the absolute maxima for
$|\mathcal{V}^{\mathrm{x}}|(\omega)$ and $|\mathcal{V}^{\mathrm{y}}|(\omega)$.
% 
In Fig. \ref{fig:up-3d-vva-1} we present the
$|\mathcal{V}^{\mathrm{a}}|(\omega)$ spectra resulting from evaluate the Eq.
\eqref{eq:vv-mag} using different polarization angles $\alpha$ in the Eq.
\eqref{eq:vab} for the \emph{up} structure. We can see that the onset of the
response is when the energy of the incoming light is the same of the gap energy.
%
From this picture we can see that for the zone between the energy range of
0.084\,eV-0.093\,eV,corresponding to the THz radiation, and polarization angles
between $30^{\circ}$ and $45^{\circ}$ is the zone where the maximum response is
held for both, $|\mathcal{V}^{\mathrm{x}}|(\omega)$ and
$|\mathcal{V}^{\mathrm{y}}|(\omega)$.
% %%%%%%%%%%%%%%%%%
% %% 1.8 eV - 2.0 eV
% %% Description of UP |V^{a}|, components and RTP
% %%%%%%%%%%%%%%%%%

In the top frames of  Figs. \ref{fig:up-vx-comp-rtp-1} and 
% 
\ref{fig:up-vy-comp-rtp-1} we present in solid lines the results of
$|\mathcal{V}^{\mathrm{x}}|(\omega)$ and $|\mathcal{V}^{\mathrm{y}}|(\omega)$,
related to the left scale, fixing the polarization angle to $\alpha=40^{\circ}$
for which the response is maximized for the \emph{up} structure. In the same
figures and frames we present in dashed lines the corresponding polar
$\theta_{a}(\omega)$ and azimuthal $\varphi_{a}(\omega)$ angles related to the
right scale. Also, in the bottom frames of those figures we present the
decomposition of $|\mathcal{V}^{\mathrm{x}}|(\omega)$ and
$|\mathcal{V}^{\mathrm{y}}|(\omega)$ in the corresponding
$\mathcal{V}^{\mathrm{xx}}(\omega)$, $\mathcal{V}^{\mathrm{xy}}(\omega)$,
$\mathcal{V}^{\mathrm{xz}}(\omega)$, and $\mathcal{V}^{\mathrm{yx}}(\omega)$,
$\mathcal{V}^{\mathrm{yy}}(\omega)$, $\mathcal{V}^{\mathrm{yz}}(\omega)$
components.
\begin{figure}[t]
    \centering
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{up} structure 
    \label{fig:up-3d-vvx-2}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-vxb-2}}
    \\
    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}|$ for \emph{up} structure 
    \label{fig:up-3d-vvy-2}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-vyb-2}}

>>>>

We preset the results for $|\mathcal{V}^{\mathrm{a}}|(\omega)$ and
$|\mathcal{V}_{\sigma^{\mathrm{b}}}|(\omega)$ for the C$_{16}$H$_{8}$-alt and
C$_{16}$H$_{8}$-up structures being both noncentrosymmetric semi-infinite carbon
systems with 50\% hydrogenation in different arrangements. The \emph{alt} system
has alternating hydrogen atoms on the upper and bottom sides of the carbon
sheet, while the \emph{up} system has H only on the upper side. We take the
hexagonal carbon lattice to be on the $xy$ plane for both structures, and the
carbon-hydrogen bonds on the perpendicular $xz$ plane, as depicted in Figs.
\ref{fig:alt-struc} and \ref{fig:up-struc}.

Using the ABINIT code \cite{gonzeCPC09} we calculated the self-consistent ground
state and the Kohn-Sham states using density functional theory in the local
density approximation (DFT-LDA) with a planewave basis. We used Hartwigsen-
Goedecker-Hutter (HGH) relativistic separable dual-space Gaussian
pseudopotentials \cite{hartwigsenPRB98} including the spin-orbit interaction
needed to calculate $\mu^{\mathrm{abcd}}(\omega)$ (Eq.
\eqref{eq:mu}), $\mathcal{V}^{\mathrm{ab}}(\omega)$ (Eq. \eqref{eq:vab}),
$|\mathcal{V}_{\sigma^{\mathrm{b}}}|(\omega)$ (Eq. \eqref{eq:vs-mag}) and
$|\mathcal{V}^{\mathrm{a}}(\omega)|$ (Eq. \eqref{eq:vv-mag}).
%
It is known that using DFT-LDA to calculate the electronic structure of
materials predict a different band gap than the obtained experimentally. A
correction for the band gap energy value can be calculated by other 
\emph{ab-initio} methods such as the GW approximation \cite{onidaRMP02} but this
is outside the scope of this paper.
% 
The convergence parameters for the calculations of our results corresponding to
the \emph{alt} and \emph{up} structures are cutoff energies of 65\,Ha and
40\,Ha, respectively. The energy eigenvalues and matrix elements were calculated
using 14452 $\mathbf{k}$ points and 8452 $\mathbf{k}$ points in the irreducible
Brillouin zone (IBZ) and present LDA energy band gaps of 0.72\,eV and 0.088\,eV,
respectively for the \emph{alt} and \emph{up} structures.

@@

In figure \ref{fig:vab-str-comp} we present a comparison of the most intense
responses resulting from evaluate the Eq. \eqref{eq:vab} for the \emph{alt} and
\emph{up} 2D structures vs. CdSe and GaAs bulk systems. As we can see from
this figure the most intense response corresponds to the \emph{up} structure
centered at 0.088\,eV corresponding to the THz radiation and reaching a
spin velocity of 87.2\,Km/s.
% 
In the other hand, for an energy range from 0.66\,eV to 3.0\,eV, corresponding
to energies of the Thz and visible radiation, all the four structures have
contributions in the same order of magnitude.
% 
Starting with the 2D structures we have that the \emph{up} structure has other
two peaks centered at 1.94\,eV and 1.97\,eV reaching spin velocities of
22.2\,Km/s and -29.7\,Km/s, respectively, and the \emph{alt} structure has two
peaks centered at 0.72\,eV and 0.91\,eV reaching spin velocities of -40.2\,Km/s
and -32.9\,Km/s, respectively.
% 
Then, for the bulk structures we have that the CdSe has only one intense
response centered at 0.91\,eV reaching a spin velocity of -26.9\,Km/s, and the
GaAs structure has a large and almost planar zone where the response is held
reaching the maximum for an incoming beam of energy of 2.31\,eV and resulting in
a spin velocity of -21.6\,Km/s.
% 
In table \ref{tab:vab-str-comp} we present the comparison of this values for the
2D and bulk structures.
%

@@

We first analyzed two energy ranges for the \emph{up} structure, the first for
an incoming energy beam from 0.0\,eV to 0.2\,eV in the THz radiation range,
where the absolute maximum of the $|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$
response is obtained and the second for an energy range from 1.80\,eV to
2.1\,eV, corresponding to the THz and visible radiation, where two local maxima
are found.

@@

Eq. \eqref{eq:vs-mag} using different polarization angles $\alpha$ in Eq.
\eqref{eq:vab}. From the figure we have that the onset of the response starts
when the energy of the incoming beam is the same of the gap energy.

@@

Making the analysis, we obtained that the zone where the maximum response is
held corresponds to a energy range of the incident beam from 0.084\,eV to
0.093\,eV and polarization angles $\alpha$ between $30^{\circ}$ and
$45^{\circ}$. Also two local maxima are held for same polarization angles but
for an energy range of the incoming beam between 1.90\,eV and 2.05\,eV.

@@

and perpendicular and the arrows are directed to the value of the response

@@

From Figs. \ref{fig:up-3d-vsz-1} and \ref{fig:up-vaz-rag-1} we have that the

@@

$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)=95.8$\,Km/s coming from the

@@

$\gamma_{\mathrm{z}}(\omega)$ are collinear being both angle $65.5^{\circ}$ and

@@

then, for variations of this magnitude in $\gamma_{\mathrm{z}}(\omega)$ the
complete range of $\alpha$ angle is included because this last is almost
constant.

@@

Now from Figs. \ref{fig:up-3d-vsz-2} and \ref{fig:up-vaz-rag-2} we have that a

@@

of $|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)=30.3$\,Km/s. This comes from a
major contribution of the $\mathcal{V}^{\mathrm{yz}}(\omega)$ component being
directed in a velocity angle $\gamma_{\mathrm{z}}(\omega)=78^{\circ}$ on the
first Cartesian Quadrant of the $xy$ plane, for the spin polarized in the $z$
direction.

@@

The most interesting case in which the spin is perpendicular to the surface of
the structure and also for the \emph{up} structure the most intense was the
presented before for which the spin is polarized in the $\mathrm{z}$ direction.
We also made the analysis for the cases when the spin polarization is directed
in the $\mathrm{x}$ and $\mathrm{y}$ direction but we do not present the
corresponding plots. For those cases we have that the absolute maxima response
is obtained for an energy of the incoming beam equal to 0.088\,eV and
polarization angle $\alpha=40^{\circ}$ resulting in values of
$|\mathcal{V}_{\sigma^{\mathrm{x}}}|(\omega)=37.4$\,Km/s and
$|\mathcal{V}_{\sigma^{\mathrm{y}}}|(\omega)=24.8$\,Km/s.

@@

For the \emph{alt} structure we analyzed the energy range for the incident beam from 0.6\,eV to 1.0\,eV, corresponding to the THz radiation, where the absolute maximum of $|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$ response is obtained.
% 
In Fig. \ref{fig:alt-3d-vsb} we present the
$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$ spectra resulting from evaluate
again Eq. \eqref{eq:vs-mag} using different polarization angle $\alpha$ in Eq.
\eqref{eq:vab} for the \emph{alt} structure. In the figure we have that the
onset of the response starts when the energy of the incoming beam is the same of
the gap energy.
% 
From this figure we found that the zone where the absolute maximum response is
held corresponds to a energy range from 0.90\,eV to 0.93\,eV and polarization
angles $\alpha$ between $120^{\circ}$ and $150^{\circ}$. Also, a local maximum
is obtained for the same polarization angles but for energies between 0.67\,eV
and 0.75\,eV.
% %%%%%%%%%%%%%%%%%
% %% 0.0 eV - 0.16 eV
% %% Description of ALT |V_{s^z}| & gamma  vs. alpha agle
% %%%%%%%%%%%%%%%%%
In the top frame of Fig. \ref{fig:alt-vaz-rag} we present in solid line the
result of evaluate $|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$, related to the
left scale, fixing the energy of the incoming beam to 0.912\,eV for which value
the response is maximized for the \emph{alt} structure. In the same figure and
frame we present with dashed line, related to the right scale, the velocity
angle $\gamma_{\mathrm{z}}(\omega)$ and in the bottom frame the corresponding
$\mathcal{V}^{\mathrm{xz}}(\omega)$ and $\mathcal{V}^{\mathrm{yz}}(\omega)$
components. Again, the circled and square boxes indicate the values for which
the polarization angle and the velocity angle are parallel and perpendicular and
with arrows are indicated the corresponding response value.
% 
From this figure and from Fig. \ref{fig:alt-3d-vsb} we have that the absolute
maximum response for the \emph{alt} structure is obtained for an incoming beam
with polarization angle $\alpha=145^{\circ}$ reaching a velocity of
$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)=43.0$\,Km/s and for the spin
polarized in the $\mathrm{z}$ direction and resulting in a velocity angle
$\gamma_{\mathrm{z}}(\omega)=50^{\circ}$ on the first Cartesian Quadrant of the
$xy$ plane. The circled box for the collinear angle corresponds for angles
$\alpha$ and $\gamma_{\mathrm{z}}(\omega)$ equal to $53.5^{\circ}$ with a value
of $|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)=12.7$\,Km/s, and the blue square
box indicates the perpendicular angles for values $\alpha=140^{\circ}$ and
$\gamma_{\mathrm{z}}(\omega)=50^{\circ}$ with a value of
$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)=43$\,Km/s. Finally we found that
for variations of $\pm0.5^{\circ}$ of those collinear and perpendicular angles,
presented with the error bars on the boxes, correspond ranges for the
polarization angle $30^{\circ} \leq \alpha \leq 70^{\circ}$ and $95^{\circ} \leq
\alpha \leq 175^{\circ}$ covering a wide range of angles because the response
angle $\gamma_{\mathrm{z}}(\omega)$ has small variations for the complete range
of the polarization angle $\alpha$.
% 
Again, for the cases in which the spin polarization is parallel to the surface
of the \emph{alt} structure was calculated but the plots are not presented here.
The absolute maxima for the case when the spin polarization is directed in the
$\mathrm{x}$ and $\mathrm{y}$ direction are obtained for an energy of the
incoming beam equal to 0.912\,eV and polarization angle $\alpha=145^{\circ}$
resulting in values of $|\mathcal{V}_{\sigma^{\mathrm{x}}}|(\omega)=27.1$\,Km/s
and $|\mathcal{V}_{\sigma^{\mathrm{y}}}|(\omega)=33.2$\,Km/s.

@@

% %%%%%%%%%%%%%%%%%
% %% 0.0 eV - 0.16 eV
% %% Description of UP |V^{a}| 3D
% %%%%%%%%%%%%%%%%%
For the \emph{up} structure we first analyzed the energy range from 0.00\,eV to
0.16\,eV, where we found the most intense response and the absolute maxima for
$|\mathcal{V}^{\mathrm{x}}|(\omega)$ and $|\mathcal{V}^{\mathrm{y}}|(\omega)$
presented in Fig. \ref{fig:up-3d-vva-1} and resulting from evaluate Eq.
\eqref{eq:vv-mag} using different polarization angles $\alpha$ in Eq.
\eqref{eq:vab} for the \emph{up} structure. We can see that the onset of the
response is when the energy of the incoming light is the same of the gap energy.
%
From this picture we can see that for the zone between the energy range of
0.084\,eV-0.093\,eV and polarization angles between $30^{\circ}$ and
$45^{\circ}$ is the zone where the maximum response is held for both,
$|\mathcal{V}^{\mathrm{x}}|(\omega)$ and $|\mathcal{V}^{\mathrm{y}}|(\omega)$.
% %%%%%%%%%%%%%%%%%
% %% 1.8 eV - 2.0 eV
% %% Description of UP |V^{a}|, components and RTP
% %%%%%%%%%%%%%%%%%

In the top frames of  Figs. \ref{fig:up-vx-comp-rtp-1} and 
% 
\ref{fig:up-vy-comp-rtp-1} we present in solid lines the results of
$|\mathcal{V}^{\mathrm{x}}|(\omega)$ and $|\mathcal{V}^{\mathrm{y}}|(\omega)$,
related to the left scale, fixing the polarization angle to $\alpha=40^{\circ}$
for which the response is maximized. In the same
figures and frames we present in dashed lines the corresponding polar
$\theta_{a}(\omega)$ and azimuthal $\varphi_{a}(\omega)$ angles related to the
right scale. Also, in the bottom frames of those figures we present the
decomposition of $|\mathcal{V}^{\mathrm{x}}|(\omega)$ and
$|\mathcal{V}^{\mathrm{y}}|(\omega)$ in the corresponding
$\mathcal{V}^{\mathrm{xx}}(\omega)$, $\mathcal{V}^{\mathrm{xy}}(\omega)$,
$\mathcal{V}^{\mathrm{xz}}(\omega)$, and $\mathcal{V}^{\mathrm{yx}}(\omega)$,
$\mathcal{V}^{\mathrm{yy}}(\omega)$, $\mathcal{V}^{\mathrm{yz}}(\omega)$
components.
\begin{figure}[t]
    \centering
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{up} structure 
    \label{fig:up-3d-vvx-2}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-vxb-2}}
    \\
    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}|$ for \emph{up} structure 
    \label{fig:up-3d-vvy-2}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-vyb-2}}
